\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}
\section{Accident \& Incident Policy}

\subsection{Accidents}

The safety of your child is paramount and I will take every measure I
can to protect your child from hurting themselves.

As a registered childminder, I am legally required to have a valid first
aid certificate. I can administer basic first aid treatment, and my
first aid box is clearly labeled and easily accessible, with contents
suitable for children. It is stored in the kitchen. Parent contact
numbers are with the first aid box.

If a child does experience an accident the following procedure will be
followed:

\begin{itemize}
\item
  ~I will comfort and reassure the injured child while making sure that
  the other children in my care are safe.~
\item
  I will assess the extent of their injuries and will carry out any
  first aid procedures that are necessary and that I have been trained
  to do.~
\item
  If deemed appropriate parents/carer will be contacted to inform them
  of the accident.~
\item
  If necessary I will call for medical support/ambulance. If I
  accompany or take a child to hospital, I will contact the parents and
  ask them to meet me at there.~
\end{itemize}

If there is an accident or an emergency and I have to accompany a child
to hospital then I will take the other children with me and contact
their parents. You will be expected to collect your child straight away.

If a serious accident occurs to a child in my setting I will contact
Ofsted as soon as I can, if possible the same day.

A record will be made of the accident and of any first aid given on an
accident form. The parent/carer will be asked to sign this form when
they arrive to collect the child. These forms will be stored in an
Accident \& Incident folder.

\subsection{Incidents}

If a child arrives at the setting with an existing injury the following
procedure will be followed:

\begin{itemize}
\item
  I will enquire with the parent/carer about the cause of the injury
  and will record these details on an incident form.~
\item
  The parent/carer will be asked to sign this record~
\end{itemize}

These forms will also be stored in the Accident \& Incident folder.

Date: 07/06/2014

~
\end{document}
