\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}
\section{Alcohol, Smoking \& Other Substances Policy}

As an Ofsted registered Childminder I work alone and will have sole
responsibility for your child whilst they are in my care. It is vital
that I am alert to any dangers and able to protect him/her.

In order to do this effectively I must not be under the influence of
alcohol or any form of drugs (including some prescription medication) If
I am prescribed medication, other than routine antibiotics I must inform
Ofsted who will make a decision as to whether I can continue to mind
whilst taking them. I will not drink any alcohol during minded hours or
immediately before. All of my over the counter medications will be
stored in a locked drawer.

As this is the childminders home, alcohol may be present on the
premises, but at all times this alcohol will be kept in a cupboard out
of any child's reach.

If you have been drinking, perhaps a work leaving party, Christmas party
or whilst entertaining clients I would prefer if you arranged for
another responsible adult to collect your child, especially if you plan
to drive home. Alternatively you may call me and I can delay the pick up
time if possible.

Smoking at all times is strictly forbidden, in all rooms. It is also
forbidden in the outdoor space. Smoking will not be tolerated, and a
parent/carer or visitor will be asked to leave if the rules are not
adhered to.

Date: 07/06/2014

~
\end{document}
