\input{includes/header.tex}

\section{Complaints Policy}

I aim to work in close partnership with all parents/carers to help meet
the needs of their children. I hope you are happy with the service that
I provide but I appreciate that there may be times when you feel that I
am not offering you and your child the service that you require. I hope
that you will feel able to discuss any concerns or issues that you have
with me directly. If you would rather not talk in front of your child
then we can arrange a more convenient time, for example in the evening
or at the weekend. I will make every effort to resolve the issue. If you
prefer, you can put the complaint formally in writing or by email to me.

Depending on the nature of the complaint, I will investigate myself or
it will be passed on to Ofsted to investigate. Complaints will be
treated sensitively. In the case of formal complaints you will be
notified of the outcome and receive a copy of any written records
regarding the complaint within 28 days.

I will keep a written record of all complaints. It will remain
confidential unless an Ofsted inspector asks to see it. I will record
the following:-

\begin{itemize}
\item
  Name of the person making the complaint~
\item
  Nature of the complaint~
\item
  Date and time of the complaint~
\item
  Action taken in response to the complaint~
\item
  Outcome of the complaint investigation (e.g. ways the service has
  improved)~
\item
  Details of the information, findings and action taken that were given
  to the complainant. ~
\end{itemize}

If you feel that you are unable to talk to me or that after talking the
matter remains unresolved, then for impartial advice you can talk in
confidence to:

The Starting Life Well Service on 0161 778 0384

If you wish to make a formal complaint then you can contact the Ofsted
helpline on 0300 123 1231

Ofsted produces guidance on concerns and complaints about childminders
and childcare providers. This is available on Ofsted's website and
provides guidance on the complainant's right to contact Ofsted.

Review Date: 31/08/2017

\input{includes/footer.tex}
