\input{includes/header.tex}

\section{Fees Policy}

Fees are payable monthly in advance. Fees are to be paid on the first of every month by standing order or bank transfer.

Fees must still be paid if your child is absent due to holidays or sickness within the school term. Please note that if your child is unwell, it is at my discretion if the child is well enough to attend the setting (see Illness \& Sickness Policy). Advice will be sought from the NHS or PHE (Public Health England) about recommended periods of exclusion due to illness, where necessary. However, if I am ill and cannot provide alternative care for your child, fees will not apply.

In the case of late payment, a fixed penalty of £10 per day will be charged. Failure to pay fees for more than 7 days will result in the immediate termination of your child's place. If necessary, I will seek legal advice.

There are two payment methods to choose between:

\subsection{System 1}

Fees are to be paid per calendar month based on the number of chargeable, term-time days\footnotemark[1]
in that month and payment should have reached my account by the 1st of each month. For example, February always has 20 working days and if half term occurs within that month, 15 days will be chargeable and £525 (£35 per day for 15 days) will be payable by the 1st of February. If your childcare provision is based on 4 days a week, then only 12 days would be chargeable in this case.

Where care provision starts part way through a given calendar month, payment will be expected before the first day of childcare to cover the remaining, chargeable days in that month. In the case where there are only a small number of days left in the month, it can be negotiated to roll them in with the next, full month's fees, paid up front before the first day of childcare.

A payment schedule for the full duration of the twelve-month contract will be provided in writing stating the amount due each month and the day by which it is to be paid. This will be agreed before the first day of childcare to ensure all parties are clear on which days are chargeable and which are not.

\subsection{System 2}

Fees are charged every calendar month (except August) in or out of term time to spread the costs evenly throughout the year and payment should have reached my account by the 1st of each month. The amount charged is based on my daily rate multiplied by the number of chargeable, term-time days in the year\footnotemark[1] divided by 11. (No fee is required on August 1st, due to the Summer holidays) 

For example, if you require full time childcare (5 days a week) and there are 195 chargeable, term-time days in the year, then the monthly charge will be:

$$£35 \times 195 \text{ days} \div 11 \text{ months} = £620.45 \text{ per month}$$

If neither of these payment systems is appropriate to your situation then feel free to discuss it with me and we can try to come up with an alternative arrangement.

\subsection{Notice Period}

Four weeks' written notice will be required in order to alter your child's sessions, for example, permanently increasing or decreasing their days. Fees will be charged as usual for these 4 weeks until alterations have been made. 

In the event that you may wish to cease your child's place at the setting, four weeks' notice is required, and fees will be charged for those four weeks, whether your child attends the setting or not.

Please note, in the case of Payment System 2, the monthly payments are averaged over term time and holiday periods, terminating the contract before 12 months may mean the amount paid to date does not reflect the number of days actually worked. In this case, the final payment will be adjusted accordingly.

It is possible to request additional sessions for your child and – providing I can accommodate your needs – I will discuss it with you and come to an arrangement. If you wish to cancel any extra sessions could you please give 24hrs notice.

Fees are as follows:

Full Day: 7:30am- 5:30pm £37
Morning Session: 7:30am-12:30pm £25
Afternoon Session 12:30pm- 5:30pm £25

If different sessions are required than those above then I will discuss fees, and the amount agreed will be on your contract and in the case of Payment System 1, on your payment schedule.

Included in your child's fees are meals, snacks, nappies, baby wipes, nappy cream and entrance to toddler groups. If you have a specific brand of nappies or cream that you wish to use on your child and you are dissatisfied with the brand offered by myself then you will have to provide your own. I do not provide formula milk. . 

I reserve the right to review my fees when the contract is renewed every 12 months.

Review Date: 31/08/2016

\begin{table}[h]
  \def\arraystretch{2.0}
  \begin{tabularx}{\textwidth}{!{\color{gray}\vrule}X!{\color{gray}\vrule}X!{\color{gray}\vrule}X!{\color{gray}\vrule}X!{\color{gray}\vrule}}
    \arrayrulecolor{gray}\hline
    Child's Name & Parent's Name & Signature & Date \\
    \hline
    ~ & ~ & ~ & \\
    \hline
    ~ & ~ & ~ & \\
    \hline
    ~ & ~ & ~ & \\
    \hline
    ~ & ~ & ~ & \\
    \hline
    ~ & ~ & ~ & \\
    \hline
    ~ & ~ & ~ & \\
    \hline
  \end{tabularx}
\end{table}

\footnotetext[1]{The number of chargeable, term-time days is calculated by taking the number of weekdays in the year and deducting any days designated as school holidays by Salford City Council.}


\input{includes/footer.tex}
