\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}
\section{Health \& Safety Policy}

The Health and Safety of your child is very important to me and I have
therefore documented the following procedures that I have in place to
support this.

\begin{itemize}
\item
  I have a daily check list which needs to be checked each day before
  the children arrive at the setting, in order to identify any hazards
  or faulty equipment. If any are discovered these will be put on a risk
  assessment form. (See Risk Assessment Policy)~
\item
  All accidents that occur will be recorded and reported to parents and
  Ofsted if necessary. (See Accident Policy)~
\item
  Children will only be offered toys that are age/stage of development
  suitable. ~
\item
  All equipment will be checked and cleaned regularly and will al be
  fitted with the correct safety harnesses to prevent accidents, for
  example high chairs and pushchairs. ~
\item
  Appropriate safety equipment is in use e.g. cupboard locks, corner
  pads etc. These are checked regularly.~
\item
  The front door will be kept locked to prevent the children opening
  it, either to exit or to greet a stranger.~
\item
  I have strict child protection guidelines in place (See Safeguarding
  Policy)~
\item
  I have procedures in place in the event of a fire. (See Fire Safety
  Policy)~
\item
  The kitchen is kept very clean, ~hygiene guidelines are followed on
  the storing of food, the fridge temperature etc. ~
\item
  I ensure that children do not have any access to any waste, the bins
  are emptied daily.~
\item
  I do not permit smoking in my home, (See Smoking Policy)~
\item
  I follow strict hygiene guidelines to prevent contamination and
  sickness (See Illness \& Sickness Policy)~
\item
  I have emergency contact details with me at all times should I need
  to contact parents.~
\item
  I will work with you to educate children about safety issues like
  crossing the road and not talking to strangers.~
\item
  I will work with you to educate children about making healthy choices
  in regards to food and physical exercise. ~
\item
  Sleeping children will be regularly monitored, using a baby monitor
  if necessary.~
\item
  I am fully insured with ~public liability insurance. ~
\end{itemize}

I welcome any discussions with you if you have any concerns about the
health and safety of your child.

Date: 07/06/2014

~
\end{document}
