\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}
\section{Illness \& Sickness Policy}

It is my policy to keep children safe when they are in my care, promote
good health and take necessary steps to prevent the spread of infection
within my setting. I will discuss with parents/carers during the
settling-in period the arrangements for the exclusion of a child should
they become ill whilst in my setting.

In order to promote good health and prevent the spread of infection I
will do the following:

\begin{itemize}
\item
  Promote hand-washing in warm, soapy water or anti-bacterial sanitiser
  gel before eating or handling food and after using the toilet.~
\item
  Promote the use of tissues for children with coughs and minor colds.~
\item
  All spillages of bodily fluids will be cleaned up immediately.~
\end{itemize}

If there is a child in my setting who becomes ill during the
child-minded period, or whom I believe has an infectious illness or
disease, for example a severe cold or stomach upset, at my discretion I
will carry out the following:

\begin{itemize}
\item
  Contact the parents as agreed to arrange for the immediate
  collection of the child. ~
\item
  Ensure the child is excluded from my setting until they have been
  well for 48 hours.~
\end{itemize}

All children in my setting who are excluded due to having an illness or
an infectious disease such as a severe cold or stomach upset will not be
allowed to return until they have been free from illness for 48 hours.
This is in order to minimise the risk of the transmission of an
infection to other children, me or members of my household.

At my discretion, if I view a child as having a mild illness -- that is
not infectious and does not impede their participation in activities --
I will permit them to the setting and will administer medicine as stated
in my Medication Policy.

I reserve the right to refuse admission of any child who is unwell or
has an infection that could be passed on.

I will contact you if my own child is not well, inform you of the
illness/symptoms and if I am able to work. This then allows you to make
an informed decision as to whether to bring your child or not.

I am happy to work when I have minor ailments such as colds, etc.
however I will not work if I have sickness or diarrhoea or any other
highly contagious infection. Continuing to work would only result in a
further spreading of the germs and I would be unable to give your child
the care they deserve. I do not charge if I am unable to work through
illness.

Date: 07/06/2014

\end{document}
