\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}
\section{Partnership With Parents Policy}

~It is very important for your child that we work together. This will
give your child consistency and continuity of care, meaning they won't
become confused about different standards of behaviour and boundaries.

As parents/carers you are the central adults in your child's life and
the ones making decisions on their behalf. I will endeavour to work
closely with you in order to carry out your wishes for your child
wherever I can. It is therefore important we have an excellent
communication system.

I appreciate that as a working parent you will be in a rush to go to
work in the mornings and in the evenings you may well be tired and need
to go as quickly as possible, so I like to use a Parent/Childminder
daily diary for communications for children who are under 3 years old. I
will complete a page each day that will include what your child has
eaten, naps, activities, milestones achieved etc. I would request that
you use this book to note down anything you feel is important about your
child's time away from the setting, for example a disturbed sleep or if
they're not feeling very well. This will help me provide the best care I
can. When a child is older than 3 years I encourage them to share these
details with you themselves, so a book is not necessary. If you wish to
continue to use a daily diary book after your child turns 3, this can be
done on request.

I am always happy to discuss your child and their care with you at any
time that is convenient to us both, whether in person or over the phone.

I would also appreciate if you could inform me if there are any changes
to contact numbers for yourselves, including work and mobile numbers and
those of your emergency contacts. It is imperative that I always have a
way to reach you in case of emergency.

As your child grows and develops events will occur that are very
important for us to discuss in order for us to work together to create
consistency for your child and for me to incorporate your wishes into my
care routine. These could include weaning, potty training, managing
behaviour, starting school etc.

If you have any concerns or issues regarding the care I am providing for
your child please do let me know and I will aim to clear up the matter
as quickly as possible.

I am very much looking forward to working in partnership with you to
care for your child and I welcome parents/carers suggestions and where
possible will implement them.

Date: 07/06/2014

~
\end{document}
