\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{amsmath}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\usepackage{titlesec}
\titlespacing*{\subsection}{0pt}{1ex plus 1ex minus .2ex}{0ex}

\usepackage{float}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}

\newcommand{\sigtable}{
\begin{table}[H]
  \def\arraystretch{2.0}
  \begin{tabularx}{\textwidth}{!{\color{gray}\vrule}X!{\color{gray}\vrule}X!{\color{gray}\vrule}X!{\color{gray}\vrule}X!{\color{gray}\vrule}}
    \hline
    Parent's Name & & Signature &  \\
    \hline
  \end{tabularx}
\end{table}
}

\section{Permission Forms}

\emph{I give consent for my child to\ldots}

Go on outings, locally and further afield (e.g. Southport, Farm, Play centre) travelling on foot, by public transport, by car or by taxi, as appropriate, with or without prior notice.

\sigtable

Be transported in/on any suitable vehicle. (Age and height appropriate restraints will be used for safety, wherever available)

\sigtable

Wear reins when out walking, depending on age and situation.

\sigtable

Use large outdoor play equipment and soft play areas, subject to suitable Risk Assessments being made.

\sigtable

Have ongoing observations made and recorded by the Childminder to follow and assess my child's development, to fulfil the requirements of the EYFS Statutory Framework, and in order to support the Childminder's professional development. These may be made in the form of written statements, photographs, audio or visual recording. My child may also appear in the records relating to other children in the Childminder's care.

\sigtable

Have sun cream applied by the Childminder or an appropriate registered assistant. The sun cream will be provided by me (the parent) and will be appropriate for my child's skin. (the recommended minimum is SPF30) Should appropriate sun cream not be provided by me, I accept that the Childminder may supply appropriate sun protection, should the need arise.

\sigtable

\pagebreak

Have sticking plasters applied, should the need arise.

\sigtable

Receive First Aid treatment, should the need arise.

\sigtable

Be bathed, should the need arise.  (For example after a messy activity)

\sigtable

Be put down for naps in a bed, cot, sofa or buggy, appropriate to their age and development.

\sigtable

Be briefly supervised by other (CRB checked) professionals, for example on an outing a fellow Childminder might look after your child whilst the Childminder takes another child to the toilet.

\sigtable

I give my consent for the Childminder to share records and information about my child with other professionals when appropriate and to seek necessary emergency medical advice or treatment for my child in the future.

\sigtable

I give my consent for the Childminder to retain some images of my child/ren, securely and safely for the purpose of continuous professional development and as evidence of activities for Ofsted. These will be kept in the setting photo book and/or stored on a secure computer and will not leave the property.

\sigtable

\input{includes/footer.tex}
