\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{titlesec}
\defaultfontfeatures{Ligatures=TeX}
% Set sans serif font to Calibri
\setsansfont{Carlito}
% Set serifed font to Cambria
\setmainfont{Caladea}
% Define light and dark Microsoft blue colours
\definecolor{MSBlue}{rgb}{.204,.353,.541}
\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
% Define a new fontfamily for the subsubsection font
% Don't use \fontspec directly to change the font
\newfontfamily\subsubsectionfont[Color=MSLightBlue]{Times New Roman}
% Set formats for each heading level
\titleformat*{\section}{\huge\bfseries\sffamily\color{MSBlue}}
\titleformat*{\subsection}{\Large\bfseries\sffamily\color{MSLightBlue}}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}%

\pagestyle{empty}

\begin{document}
\section{Risk Assessment Policy}

The purpose of this policy is to highlight the ways in which I will
record any risks within the setting, and how to minimise or eliminate
that risk.

A daily check list is completed to ensure that equipment is clean and
safe for the children to use and that the setting is clean and suitable
for the children to play in. During these checks if any new risks are
discovered they will be put onto a risk assessment form and dealt with
accordingly, to either minimise the risk or eliminate it. A complete
risk assessment of the setting is completed annually, and all rooms that
are accessed by children and their contents are assessed for their risk.
Any items that have been gained or altered will be assessed accordingly.

Equipment will be checked regularly and children will be provided with
age appropriate toys at all times.

A risk assessment will be completed before an outing to a new
destination takes place. This will be reviewed throughout the day,
eliminating risks to the children. When a downloadable risk assessment
is available this will be used as a guidance.

Correct adult to child ratios will be observed at all times, to ensure
the best quality of supervision.

Date: 07/06/2014

Review Date: 07/06/2015

~
\end{document}
