\input{includes/header.tex}

\section{Sun Protection Policy}

The damaging effects of sun exposure on the skin of young children has recently been well documented. I will do everything I can, working in partnership with you, to ensure that your child is protected.

I will need you to provide me with:
\begin{itemize}
\item Sun cream that is suitable for your child (high factor, protecting against UVA & UVB rays)
\item Sun hat (wide brimmed to cover the neck, if possible)
\end{itemize}

I will need these to be provided at the beginning of April and will keep them at the setting until the end of September. These will be labelled with your child's name and for their sole use.

What I will do to protect your child:

\begin{itemize}
\item I will ensure that I apply the sun cream before we leave the house on a sunny day and frequently reapply it throughout the day. 
\item I will insist that your child keeps their hat on whilst under direct sunlight. 
\item I will avoid spending prolonged periods of time outdoors during the hottest part of the day, and protect your child when on outings by keeping the shade over the pushchair. (If applicable) 
\item I will encourage your child to drink water regularly to prevent dehydration. 
\end{itemize}

I will require you to sign a form giving me permission to apply the sun cream that you have provided. If you have not provided any sun cream then I will use an appropriate replacement. I will require you to sign a permission form for this eventuality also. If you do not give me permission to put sun cream on your child then unfortunately I will not be able to offer your child a place at the setting.

Review Date: 31/08/2016

\input{includes/footer.tex}
